---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GuiRBioDiv

<!-- badges: start -->
<!-- badges: end -->

The goal of GuiRBioDiv is to provide some wrapper functions to speed-up alpha diversity analyses of metabarcoding datasets.

It features:
 -  `alpha_residual` for correction of sequencing depth bias for alpha diversity indices with linear models
 -  `endemic` to identify species/OTUs/ASVs uniquely found in one geographic region
 -  `transformTukey2` to transform numeric vectors to more normally distributed values with Tukey's ladder of power method


## Installation

`GuiRBioDiv` can be installed from GitHub like so:

``` r
install.packages("remotes")
remotes::install_github("lentendu/GuiRBioDiv")
```

## Example

Compute Hill numbers and correct for sequencing depth bias:

```{r example}
library(GuiRBioDiv)
alphadiv<-alpha_residual(mat_exa, index="hill", inform=T)
```
